\documentclass[11pt]{article}
\usepackage{ifthen}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hevea}
\input{synrc.hva}
%HEVEA \loadcssfile{synrc.css}
\begin{document}

\title{Github}
\author{Maxim Sokhatsky}

%HEVEA \begin{divstyle}{selectedwrapper}
%HEVEA \begin{divstyle}{wrapper}


%HEVEA \begin{divstyle}{block}
\section*{Data Framework}
\paragraph{}
KVS is Key-Value Storage Data Framework that provide high-level API for handling
social data like Users, Feeds, Comments, etc. It is designed with sequential consistency in mind.

More: \footahref{http://synrc.github.io/kvs/}{synrc.github.io/kvs}
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{block}
\section*{Message Queue Library}
\paragraph{}
MQS is RabbitMQ client library that handles conections, channels,
subscriptions has its own routing interface that you can use for building
sophisticated subscriptions topology. It also supports RPC over MQ.

More: \footahref{http://synrc.github.io/mqs/}{synrc.github.io/mqs}
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{block}
\section*{\footahref{http://synrc.com/framework/web}{Web Framework}}
\paragraph{}
Nitrogen 2 Optimized. Binary page construction. Binary data transfer.
Websocket async interface for page updates. No processes spawn, works
within Cowboy processes. Page render is 2X faster than original Nitrogen.

More: \footahref{http://synrc.github.io/n2o/}{synrc.github.io/n2o}
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{block}
\section*{Feed Server}
\paragraph{}
Feed Server is node of user workers region. It handles all MQ
requests for write operations for user's data and other APIs.
Also it acts as distributed cache for user feeds and other list chains.

More: \footahref{http://synrc.github.io/feed_server/}{synrc.github.io/feed_server}
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{block}
\section*{\footahref{http://synrc.com/framework/snmp}{SNMP Framework}}
\paragraph{}
In aestetic of HAL 9000 Web Site application to monitor Synrc clusters.
Supports extendable set of plugins to display information. See Showcase for details.
Also look at snmp_agent application that you should embedd in you services.

More: \footahref{https://github.com/kakaranet/monitor}{framework/snmp}
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{block}
\section*{Directory Server}
\paragraph{}
Directory Server is a distributed storage that can handle tens of
millions online user requests. 
In its core as most of LDAP servers Synrc Directory is based on
key-value distributed data store, DHT.

More: \footahref{http://synrc.github.io/directory_server/}{synrc.github.io/directory_server}
%HEVEA \end{divstyle}


%HEVEA \begin{divstyle}{block}
\section*{Category Theory}
\paragraph{}
Here is a set of Books on Category Theory, Dependent Types, Lambda and Process Calculus.

More: \footahref{http://synrc.com/publications/cat}{publications/cat}
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{block}
\section*{\footahref{labs.htm}{Geek Labs}}
\paragraph{}
Synrc Research Center archived all information about BeOS operating system 
including CD images and have dedicated page for this purposes and also some
other stuff like PL/1 .NET compiler Windows Sync application and XMPP Chat for BeOS, Charity Language and Io.
%HEVEA \end{divstyle}

%HEVEA \end{divstyle}
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{clear}{~}\end{divstyle}

%HEVEA \begin{divstyle}{nonselectedwrapper}
%HEVEA \begin{divstyle}{verywidecol}

\footahref{feedback.htm}{Contact Us}

%HEVEA \end{divstyle}
%HEVEA \end{divstyle}

\end{document}
