\documentclass[11pt]{article}
\usepackage{ifthen}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hevea}
\input{synrc.hva}
%HEVEA \loadcssfile{synrc.css}
\begin{document}
%HEVEA \rawhtmlinput{templates/n2o-banner.htx}
\title{synrc}
\author{Maxim Sokhatsky}
%HEVEA \begin{divstyle}{selectedwrapperlight}
%HEVEA \begin{divstyle}{wrapper}
%HEVEA \begin{divstyle}{block}
\section*{\footahref{http://voxoz.com}{Voxoz Platform}}
\paragraph{}
Build your awesome LXC/XEN Erlang Cloud using
famous \footahref{https://docker.io}{Docker} and
glorious \footahref{https://erlangonxen.org}{Erlang on Xen} technology.
Run you first Erlang App Store demo web application with SSH access in 4 clicks.
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{block}
\section*{\footahref{apps.htm}{N2O Stack}}
\paragraph{}
N2O WebSocket application server not only fastest Erlang web
framework that introduce zero additional {\bf gen_server} layer for chanells.
But also provides client JavaScript library that equals triple MSS size.
It is in TOP-15 Erlang projects and ready for highly available
real world applications running on top of fastest Erlang web server {\bf cowboy}.
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{block}
\section*{\footahref{news/index.htm}{Synrc Events}}
\paragraph{}
Train your erlang engineers with our solid Erlang experience.
Latest Events:
\paragraph{}
\footahref{news/2014/california.htm}{San Francisco USA 6 Mar 2014}
\paragraph{}
\footahref{news/2014/brug.htm}{Minsk Belarus 25 Jan 2014 }
\paragraph{}
\footahref{https://mostlyerlang.com/2013/12/18/024-voxoz/}{Mostly Erlang 18 Dec 2013}
%HEVEA \end{divstyle}
%HEVEA \end{divstyle}
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{selectedwrapper}
%HEVEA \begin{divstyle}{wrapper}
%HEVEA \begin{divstyle}{block}
\section*{Windows, Linux, Mac}
\paragraph{}
We put some power to seamless support and sleek experience on Windows, Linux and Mac platforms.
Thatnks to MAD build and deploy tool you can package all your site with all static into a single file
that can be atomically deployed to any system with Erlang installed or build unix
executable with built-in LING.
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{block}
\section*{Enterprise Business}
\paragraph{}
For business customer we have separate line of products like workflows engines,
processing languges and processing repositories, distributed linearizable
databases with XA protocol and automatic business forms generation with N2O.
Checkout \footahref{http://spawnproc.com}{Spawnproc} ogranization.
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{block}
\section*{Consulting}
\paragraph{}
We provide code review, prototyping, support and consulting services since 2005.
``No Bullshit'' services already provided to a line of customers who put N2O
and companion libraries to core of their business.
%HEVEA \end{divstyle}

%HEVEA \end{divstyle}
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{clear}{~}\end{divstyle}

%HEVEA \begin{divstyle}{nonselectedwrapper}
%HEVEA \begin{divstyle}{verywidecol}
\section*{Full Stack Erlang Applications}
\paragraph{}

Staring from {\bf kernel} and {\bf stdlib} we distilled and refined Erlang Base Library
fixing by the way such things as bundling creation, like OTP releases
but in form of {\bf escript} files, providing abstract ETS based filesystem layer,
compact and embadable buildtool {\bf mad}, and native file-system listener {\bf fs}
used by Elixir community. We also have our own {\bf gen_server} replacement and much more.

In the storage API we have {\bf kvs} abstract term database that is driven by community and
has MongoDB, Riak, Mnesia, Redis, SQL and Filesystem backends. It provides schema and
versioning and powers enterpise and banking. As the transactional log library {\bf disk_log}
replacement can utilise half of the SSD drive throughput.

Supervised hashtable of servers {\bf ring} and transactional layer {\bf xa} dedicated
for builing scalabale distributed processing engines.

\footahref{research.htm}{Lay cards on the Table}

%HEVEA \end{divstyle}
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{clear}{~}\end{divstyle}

\end{document}
