\documentclass[11pt]{article}
\usepackage{ifthen}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hevea}
\input{synrc.hva}
%HEVEA \loadcssfile{synrc.css}
\begin{document}

\title{Showcase}
\author{Maxim Sokhatsky}

%HEVEA \begin{divstyle}{selectedwrapper}
%HEVEA \begin{divstyle}{wrapper}

%HEVEA \begin{divstyle}{block}
\section*{Data Consulting}
\paragraph{}
    Tired with SQL and ORM mapping? Feel the power with typed Erlang
    records format as a native storage with gateway to Filysystem,
    Riak, mongoDB, Mnesia, KAI and SQL backends using our
    \footahref{https://synrc.github.io/kvs/}{KVS} Abstract Database with REST interface.
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{block}
\section*{System Architect}
\paragraph{}
    Want Erlang to power your enterprise business?
    Just check our Spawnproc stack which is already used for
    serving millions of customers in Eastern Europe.
    \footahref{http://spawnproc.github.io/bpe/}{BPE} workflow engine and
    \footahref{http://spawnproc.github.io/upl/}{UPL} processing language
    are undestood and yet manageable.
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{block}
\section*{Web Applications}
\paragraph{}
    Forget about fat JSON and XML exchange.
    We use tiny binary BERT messages on top of robust and extensible
    N2O protocol for IoT and WebSoсket applications.
    Our reference implementation \footahref{http://synrc.space/apps/n2o}{N2O} WebSocket Application Server is known as most powerful Erlang Web Framework.
%HEVEA \end{divstyle}

%HEVEA \end{divstyle}
%HEVEA \end{divstyle}
%HEVEA \begin{divstyle}{clear}{~}\end{divstyle}

%HEVEA \begin{divstyle}{nonselectedwrapper}
%HEVEA \begin{divstyle}{verywidecol}
\section*{Voxoz Erlang Cloud Control Panel}
\paragraph{}
    Enter the future now with Voxoz cloud platform which is able to run
    Elrang virtual machine on top of raw hardware in Xen environment.
    LING virtual machine has also ports to POSIX, ARM and MIPS platforms.
    Or you can run BEAM virtual machine in docker. The application is a file.
    As simple as that. This is Voxoz.

%HEVEA \rawhtmlinput{templates/voxoz.htx}

\@fontsize{3}{Mentor: Vladimir Kirillov \@br Parnerts: Cloudozer, LLC. \@br}

%HEVEA \end{divstyle}
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{nonselectedwrapper}
%HEVEA \begin{divstyle}{verywidecol}
\section*{Skyline App Store}
\paragraph{}
    Don't know how to start using N2O and need more sophisticated project that N2O sample?
    Just clone \footahref{http://synrc.github.io/skyline/}{Skyline} web shop sample with AVZ
    avtoriazation for Google, Facebook, Github, Twitter and Microsoft providers.
    Skyline App Store is Voxoz and Xen ready application. It uses N2O, KVS,
    Bootstrap style with node js tools for JavaScript minification and LESS assembling.

%HEVEA \rawhtmlinput{templates/skyline.htx}

\@fontsize{3}{Backend: Maxim Sokhatsky \@br Design: Andrii Zadorozhnii \@br}

%HEVEA \end{divstyle}
%HEVEA \end{divstyle}


%HEVEA \begin{divstyle}{nonselectedwrapper}
%HEVEA \begin{divstyle}{verywidecol}
\section*{Scalable Web and Gaming Platform}
\paragraph{}
    For the Turkish audience we created scalable distributed system using Erlang, Riak,
    Cowboy, RabbitMQ, N2O, GlusterFS, NGINX and other tools.
    Please read the technical description
    \footahref{https://speakerdeck.com/5ht/kakaranet-presentation}{Kakaranet Tech}.
    We have implemented Facebook, Paypal, Credit Cards, Mobile and Wired Payments,
    Mail system support and SNMP monitoring tools. We've done full HTML5 optimization
    with A marks for both Yahoo! YSlow and Google Page Speed. Kakaranet is lineary scalable
    Facebook-like application with feeds, subscriptions and messaging along with
    powerful turn-based board games engine. The heart of the system the RabbitMQ
    cluster. The System runs on top of Riak cluster with easy maintenance from Web
    and supports hot code reload using ACTIVE native file system listener.

%HEVEA \rawhtmlinput{templates/kakaranet.htx}

\@fontsize{3}{Mentor: Maxim Sokhatsky \@br Game Server: Serge Polkovnikov \@br}

\paragraph{}
    Full size of codebase is fit 2.88MB floppy disk and is quite managable yet.
    The system inside is essentially built upon binary protocols AMQP, BER
    except content delivery to Web clients which is in fact gzipped.

%HEVEA \end{divstyle}
%HEVEA \end{divstyle}


%HEVEA \begin{divstyle}{nonselectedwrapper}
%HEVEA \begin{divstyle}{verywidecol}
\section*{SNMP Monitoring System}
\paragraph{}
    For our servers we created open-source Erlang based SNMP monitoring tools
    with clear and simple interface which allows you to feel the heartbeat of
    your system on any device despite the screen size.

%HEVEA \rawhtmlinput{templates/hal.htx}

\@fontsize{3}Mentor: Andrew Zadorozhny \@br Design: Alex Kalenuk

%HEVEA \end{divstyle}
%HEVEA \end{divstyle}

%HEVEA \begin{divstyle}{nonselectedwrapper}
%HEVEA \begin{divstyle}{verywidecol}
\section*{SVG and WebSockets}
\paragraph{}
    For the HTML5 web platform and pure JavaScript client-side we would recommend to use
    SVG and WebSockets. N2O provides all facilities for dealing with DOM and fast binary
    real-time WebSocket channels. We don't use Xml HTTP Requests since 2010.

%HEVEA \end{divstyle}
%HEVEA \end{divstyle}


%HEVEA \begin{divstyle}{nonselectedwrapper}
%HEVEA \begin{divstyle}{verywidecol}
\section*{Binary Protocols}
\paragraph{}
    We are trying to build our products and services around single core of technologies.
    We believe that focusing on understandable and manageable,
    proven in industry technologies will bring significant benefits to all users.
    We have chosen set of technologies that have proved its maturity, clarity and efficiency.
    We oriented on strong and mature binary protocols and data formats such as BER and ASN.1.
    Please read more on \footahref{http://5ht.co}{N2O PROTOCOL} at dedicated site.

\footahref{apps.htm}{Follow The Source}

%HEVEA \end{divstyle}
%HEVEA \end{divstyle}


%HEVEA \begin{divstyle}{clear}{~}\end{divstyle}


\end{document}
